Plotting cropland biases

### 2015-06-04 Rmd/compare-landcover.Rmd
1. New version of figures, with boxplot version of 1 km pushed to separate figure for supplemental. 2. Pushed paper related material (figures, etc) to new paper folder. 2. Tested out polynomial regressions in biases in compare-landcover.Rmd

```{r, eval = FALSE}
salc <- raster(full_path(p_data, "sa_ag_masked.tif")) * 100
globsa_list_sum <- lapply(full_path(p_data, dir(p_data, "globSA*.*1kmrect_sum.tif")[c(2:3, 1)]), raster)
modsa_list_sum <- lapply(full_path(p_data, dir(p_data, "mod_1*.*1kmrect_sum.tif")[c(2:3, 1)]), raster)
glcsa <- raster(full_path(p_data, "glcsa_masked.tif"))
geow <- raster(full_path(p_data, "geowikisa_masked.tif"))
lclist <- c(salc, globsa_list_sum, modsa_list_sum, glcsa, geow)  # into list
names(lclist) <- c("sa30", "globmin", "globmu", "globmax", "modmin", "modmu", "modmax", "glcsh", "geow")
```

@@

```{r, eval = FALSE}
# Aggregate rasters
#fact <- c(5, 10, 25, 50, 100, 200, 300)
fact <- 25
lc_agg <- aggregate_rast_list(fact, lclist)   # landcover rasters 
gti_agg <- aggregate_rast_list(fact, gti)  # GTI rasters

@@

```
[[back to top]][Overview]
### Bias as function of cropcover
+ First create NA mask at 1 km resolution, then weighting raster based on number of non-NA cells in each aggregated pixel, and then "bin" rasters, where each category represents a different cropland fractional cover range (0-5%, 5-10%, etc) 
```{r, eval = FALSE}
# NA mask and weights
namask <- !is.na(gti[[1]])  
area_wgts <- aggregate_rast_list(fact, list(namask), fun = sum)
namask[namask == 0] <- NA
writeRaster(namask, filename = full_path(p_data, "namask.tif"), overwrite = TRUE)

# cropland cover bins
binv <- seq(0, 100, 5)
gti_bins <- lapply(gti_agg, function(x) lapply(x, function(y) cut(y, breaks = binv, include.lowest = TRUE)))
```

@@

>>>>

```{r, eval = FALSE}
salc <- raster(full_path(p_data, "sa_ag_masked.tif")) * 100
globsa_list_sum <- lapply(full_path(p_data, dir(p_data, "globSA*.*1kmrect_sum.tif")[c(2:3, 1)]), raster)
fnames <- full_path(p_data, dir(p_data, "mod_1*.*1kmrect_sum.tif")[c(2:3, 1)])
modsa_list_sum <- lapply(fnames, raster)
glcsa <- raster(full_path(p_data, "glcsa_masked.tif"))
geow <- raster(full_path(p_data, "geowikisa_masked.tif"))
lclist <- c(salc, globsa_list_sum, modsa_list_sum, glcsa, geow)  # into list
names(lclist) <- c("sa30", "globmin", "globmu", "globmax", "modmin", "modmu",
                   "modmax", "glcsh", "geow")
```

@@

```{r, eval = FALSE}
# Aggregate rasters
#fact <- c(5, 10, 25, 50, 100, 200, 300)
#fact <- 25
lc_agg <- aggregate_rast_list(fact, lclist)   # landcover rasters 
gti_agg <- aggregate_rast_list(fact, gti)  # GTI rasters

@@

```
[[back to top]][Overview]

### Bias as function of cropcover
+ First create NA mask at 1 km resolution, then weighting raster based on number of non-NA cells in each aggregated pixel, and then "bin" rasters, where each category represents a different cropland fractional cover range (0-5%, 5-10%, etc) 
```{r, eval = FALSE}
# NA mask and weights
namask <- !is.na(gti[[1]])
area_wgts <- aggregate_rast_list(fact, list(namask), fun = sum)
namask[namask == 0] <- NA
writeRaster(namask, filename = full_path(p_data, "namask.tif"), 
            overwrite = TRUE)

# cropland cover bins
binv <- seq(0, 100, 5)
gti_bins <- lapply(gti_agg, function(x) {
  lapply(x, function(y) cut(y, breaks = binv, include.lowest = TRUE))
})
```

@@

+ Collected absolute differences with weights for regression plots. Test first on 25 km
```{r, eval=FALSE}
gti_2011_25 <- raster(full_path(p_data, "gti_2011_25km.tif"))
snms2 <- c("sa30", "modmu", "globmu", "geow")
km25 <- stack(lapply(dlist_abs[snms2], function(x) x$f25$g2011))
s <- stack(list(area_wgts$f25[[1]], gti_2011_25, km25))
# s <- s[[-10]]
library(agroEcoTradeoffs)
DT <- as.data.table.raster(s)
DT <- DT[!is.na(namask), ]
setnames(DT, "gti_2011_25km", "A")
DTL <- do.call(rbind, lapply(3:ncol(DT), function(x) {
  DTS <- DT[, c(1, 2, x), with = FALSE]
  setnames(DTS, colnames(DT)[x], new = "D")
}))
head(DTL)
DTL[, plot(A, D, pch = 20, cex = 0.1)]
dlm <- lm(D ~ poly(A, degree = 2), weights = namask, data = DTL)
lines(predict.lm(dlm, newdata = data.frame("A" = 1:100)))

DT[, plot(A, geow, pch = 20, cex = 0.1)]
dlm <- lm(geow ~ poly(A, degree = 2), data = DT)
lines(predict.lm(dlm, newdata = data.frame("A" = 1:100)))

### 2015-06-04 Rmd/landcover-bias-plots.Rmd
1. New version of figures, with boxplot version of 1 km pushed to separate figure for supplemental. 2. Pushed paper related material (figures, etc) to new paper folder. 2. Tested out polynomial regressions in biases in compare-landcover.Rmd

# Paths
p_root <- proj_root("SAcropland")
p_fig <- full_path(p_root, "SAcropland/external/figures/")
p_data <- full_path(p_root, "SAcropland/external/ext_data/")

@@

Plot maps of biases at different resolutions, for publication output (and display here). To avoid the visual distortion of NA areas filled in by larger levels of aggregation, each aggregated difference must be disaggregated first and then masked before plotting.   
```{r, eval = FALSE}
namask <- raster(full_path(p_data, "namask.tif"))
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data, excluding Modis and GlobCov extremes
lev <- c("f1", "f25", "f50", "f100")  # just show four levels

@@

<p align="center"><img src="../external/figures/bias_map.pdf" width="400px"></p>

@@

### Bias in relation to field density

```{r, eval = FALSE}
btype <- c("bias_act.pdf", "bias_abs.pdf")
# plot matrix
nc <- 4
m <- matrix(rep(c(rep(1, 8), rep(2, 8), rep(3, 8), rep(4, 8)), 2), nrow = 6, ncol = 32, byrow = TRUE) 
m2 <- unlist(lapply(seq(5, by = 1, length = 8 * 4), function(x) rep(x, nc)))
m3 <- do.call(rbind, lapply(seq(1, length(m2), by = 8 * nc), function(x) {
  do.call(rbind, rep(list(m2[x:(x + 8 * nc - 1)]), nc))
})) 
cols <- c("red", "orange3", "green4", "blue", "yellow")
bcol <- c("grey50", "grey50", "grey50", "grey")
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")
levnms <- paste(gsub("f", "", lev), "km")
fcol <- "grey"
lev <- names(dstats_all$act$sa30)
lvec <- seq(5, 100, 5)
pp <- list("x" = c(-2, 21), "y" = c(0, 0), 
           "x21" = list(c(0, 9), c(9, 21)),
           "y2" = list(c(seq(-100, -10, 10), seq(10, 100, 10)), seq(10, 100, 10)), 
           "y1lwd" = list(2, 1),  
           "y2lwd" = 0.5, #c(1, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 1, 0.5, 1),
           "y2lc" = list(c("black", rep("grey80", 4), "black", rep("grey80", 4), 
                           rep("grey80", 4), "black", rep("grey80", 4), "black"),
                         rep("grey80", 10)),
           "y3lwd" = rep(2, length(lev)), 
           "yl" = list(c(-100, 100), c(0, 100)), "yl2" = list(c(-40, 40), c(0, 60)), 
           "xl" = c(1, 20),
           "xaxl" = unlist(lapply(seq(5, 100, 10), function(x) c(x, " "))),
           "xaxl2" = ifelse(seq(5, 100, 5) %in% c(25, 50, 75), seq(5, 100, 5), " "),
           "yax1" = list(seq(-100, 100, 50), seq(0, 100, 20)), 
           "yax2" = list(unlist(lapply(seq(-40, 40, 20), function(x) c(" ", x)))[-1], 
                         unlist(lapply(seq(0, 60, 20), function(x) c(" ", x)))[-1]),
           "yaxp" = list(-100, 0), 
           "ycol" = c("grey70"))  # plot parameters

for(bt in 1:2) {
  pdf(full_path(p_fig, btype[bt]), width = 7, height = 7)
  lmat <- rbind(m, m3)
  l <- layout(lmat)
  par(mar = c(3, 0, 0, 0), oma = c(3, 4, 2, 2))
  snms <- names(dstats_all[[bt]])[names(dstats_all[[bt]]) != "glcsh"]
  dset <- dstats_all[[bt]][snms]
  for(i in 1:length(snms)) {
    #bt <- 1
    d <- dset[[snms[i]]]$f1
    n <- nrow(d)
    plot(pp$x, pp$y, ylim = pp$yl[[bt]], xlim = pp$xl, type = "l", 
         lwd = pp$y1lwd[[bt]], axes = FALSE, 
         xlab = "", ylab = "")
    if(i == 1) axis(2, at = pp$yax1[[bt]], labels = pp$yax1[[bt]], las = 2, 
                    mgp = c(1, 0.6, 0))
    axis(1, at = 1:20, labels = pp$xaxl, las = 2, mgp = c(1, 0.4, 0), tcl = -0.3, 
         pos = pp$yaxp[[bt]], cex = 0.8)
    for(z in 1:length(pp$y2[[bt]])) lines(pp$x, rep(pp$y2[[bt]][z], 2), 
                                          lwd = pp$y2lwd, col = pp$y2lc[[bt]][z])
    for(k in 1:n) {
      a <- seq(grep("2.5", colnames(d)), by = 1, length.out = 6)
      if(!is.na(d[k, 2])) boxplot_v(k, d[k, a], n, 150, 10, bcol, fcol, pcex = 0.5, 
                                    lwd = c(1, 0.5, 2))
    }
    lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = 3)
    if(i == 1) mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, 
                     line = 2.2, cex = 0.8)
    mtext(lcnms[i], side = 3, line = 0, col = cols[i])
  }
  mtext("% cropland", side = 1, outer = TRUE, line = -36.7, cex = 0.8)
  par(mar = c(0.5, 0, 0.5, 0.3))
  for(i in 1:length(snms)) {
    highcounter <- rep(0, length(lev))
    for(j in 1:length(lev)) {
      plot(pp$x, pp$y, ylim = pp$yl2[[bt]], xlim = pp$xl, type = "l", lwd = 1, 
           axes = FALSE, xlab = "", ylab = "", xaxs = "i")
      for(z in 1:length(pp$y2[[bt]])) {
        lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd = pp$y2lwd, col = pp$y2lc[[bt]][z])
      }
      d <- dset[[i]][[lev[j]]]
      n <- nrow(d)
      lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = pp$y3lwd[j])
      muv <- round(mean(d[, 8], na.rm = TRUE))
      if(j == length(lev)) {
        mtext(expression(mu), side = 1, cex = 0.8, col = "grey10", 
              line = ifelse(bt == 1, -1.5, -1.8), adj = 1.1)
      }
      text(10, pp$yl2[[bt]][1] + 10, labels = muv, cex = 1.3, col = "grey10")
      toohigh <- which(d[, "mu"] > pp$yl2[[bt]][2])
      if(length(toohigh) > 0) {
        highcounter[j] <- 1
        xi <- toohigh[which.max(d[toohigh, "mu"])]
        text(xi, y = pp$yl2[[bt]][2], labels = round(d[xi, "mu"]), col = "grey50", 
             xpd = NA)
      }
      if(j == length(lev)) {
        if(sum(highcounter) > 0) mtext("max", side = 3, cex = 0.7, col = "grey50", 
                                       line = -0.7, adj = 1.1)
      }
      if(j == 1) {
        axis(2, at = seq(pp$yl2[[bt]][1], pp$yl2[[bt]][2], 10), 
             labels = pp$yax2[[bt]], las = 2, mgp = c(1, 0.6, 0))
      }
      if(i == 1) mtext(levnms[j], side = 3, line = -0.4, cex = 0.8)
      axis(1, at = c(1, 5, 10, 15, 20), labels = rep("", 5), mgp = c(1, 1, 0), 
           tcl = -0.7, lwd.ticks = 1.2, 
           pos = pp$yl2[[bt]][1])
      axis(1, at = 1:20, labels = rep("", 20), las = 2, mgp = c(1, 0.4, 0), 
           tcl = -0.3, pos = pp$yl2[[bt]][1])
      if(i == length(snms)) {
        axis(1, at = 1:20, labels = pp$xaxl2, las = 2, mgp = c(1, 0.8, 0), 
             tcl = -0.3, pos = pp$yl2[[bt]][1])
      }
    }
  }
  mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, line = 2.2, 
        cex = 0.8, outer = TRUE, adj = 0.35)
  mtext("% cropland", side = 1, outer = TRUE, line = 1.5, cex = 0.8)
  dev.off()
}

>>>>

# Paths
p_root <- proj_root("SAcropland")
p_fig <- full_path(p_root, "SAcropland/paper/figures/")
p_data <- full_path(p_root, "SAcropland/external/ext_data/")

@@

Plot maps of biases at different resolutions, for publication output (and display here). To avoid the visual distortion of NA areas filled in by larger levels of aggregation, each aggregated difference must be disaggregated first and then masked before plotting.   
```{r, eval = FALSE}
namask <- raster(full_path(p_data, "namask.tif"))
snms <- c("sa30", "globmu", "modmu", "geow")  # all lc data (no MOD/GC extremes)
lev <- c("f1", "f25", "f50", "f100")  # just show four levels

@@

<p align="center"><img src="../paper/figures/bias_map.pdf" width="400px"></p>

@@

### Bias in relation to field density
1. Supplementary figures - bias plots at 1 km with boxplots.

```{r, eval = FALSE}
#btype <- c("bias_act.pdf", "bias_abs.pdf")
# plot matrix
nc <- 4
m <- matrix(rep(c(rep(1, 8), rep(2, 8), rep(3, 8), rep(4, 8)), 2), nrow = 6, 
            ncol = 32, byrow = TRUE) 
cols <- c("red", "orange3", "green4", "blue", "yellow")
bcol <- c("grey50", "grey50", "grey50", "grey")
lcnms <- c("SA LC", "GlobCover", "MODIS", "Geowiki")
fcol <- "grey"
lev <- names(dstats_all$act$sa30)
lvec <- seq(5, 100, 5)
pp <- list("x" = c(-2, 21), "y" = c(0, 0), 
           "x21" = list(c(0, 9), c(9, 21)),
           "y2" = list(c(seq(-100, -10, 10), seq(10, 100, 10)), 
                       seq(10, 100, 10)), 
           "y1lwd" = list(2, 1),  
           "y2lwd" = 0.5, #c(1, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 1, 0.5, 1),
           "y2lc" = list(c("black", rep("grey80", 4), "black", rep("grey80", 4), 
                           rep("grey80", 4), "black", rep("grey80", 4),"black"),
                         rep("grey80", 10)),
           "yl" = list(c(-100, 100), c(0, 100)), 
           #"yl2" = list(c(-40, 40), c(0, 60)), "xl" = c(1, 20),
           "yl2" = c(-20, 60), "xl" = c(1, 20),
           "xaxl" = unlist(lapply(seq(5, 100, 10), function(x) c(x, " "))),
           "xaxl2" = ifelse(seq(5, 100, 5) %in% c(25, 50, 75), seq(5, 100, 5), 
                            " "),
           "yax1" = list(seq(-100, 100, 50), seq(0, 100, 20)), 
           #"yax2" = list(
            # unlist(lapply(seq(-40, 40, 20), function(x) c(" ", x)))[-1], 
            # unlist(lapply(seq(0, 60, 20), function(x) c(" ", x)))[-1]),
           #"yaxp" = list(-100, 0), 
           "ycol" = c("grey70"))  # plot parameters

pdf(full_path(p_fig, "biases_1km.pdf"), width = 7, height = 5)
lmat <- rbind(m, m + max(m))
l <- layout(lmat)
par(mar = c(3, 0, 0, 0), oma = c(1, 4, 2, 2))
for(bt in 1:2) {
  snms <- names(dstats_all[[bt]])[names(dstats_all[[bt]]) != "glcsh"]
  dset <- dstats_all[[bt]][snms]
  for(i in 1:length(snms)) { i
    d <- dset[[snms[i]]]$f1
    n <- nrow(d)
    plot(pp$x, pp$y, ylim = pp$yl[[bt]], xlim = pp$xl, type = "l", 
         lwd = pp$y1lwd[[bt]], axes = FALSE, 
         xlab = "", ylab = "")
    if(i == 1) axis(2, at = pp$yax1[[bt]], labels = pp$yax1[[bt]], las = 2, 
                    mgp = c(1, 0.6, 0))
    axis(1, at = 1:20, labels = pp$xaxl, las = 2, mgp = c(1, 0.4, 0), 
         tcl = -0.3, pos = pp$yaxp[[bt]], cex = 0.8)
    for(z in 1:length(pp$y2[[bt]])) {
      lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd =pp$y2lwd, col = pp$y2lc[[bt]][z])
    }
    for(k in 1:n) {
      a <- seq(grep("2.5", colnames(d)), by = 1, length.out = 6)
      if(!is.na(d[k, 2])) {
        boxplot_v(k, d[k, a], n, 150, 10, bcol, fcol, pcex = 0.5, 
                  lwd = c(1, 0.5, 2))
      }
    }
    lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = 3)
    if(i == 1) mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, 
                     line = 2.2, cex = 0.8)
    if(bt == 1) mtext(lcnms[i], side = 3, line = 0, col = cols[i])
  }
}
mtext("% cropland", side = 1, outer = TRUE, line = -1, cex = 0.8)
dev.off()
```

2. Bias with scale
```{r, eval=FALSE}
lev <- lev[!lev %in% c("f5", "f300")]
levnms <- paste(gsub("f", "", lev), "km")
m2 <- unlist(lapply(seq(1, by = 1, length = length(lev) * 4), function(x) {
  rep(x, nc)
}))
m3 <- do.call(rbind, lapply(seq(1, length(m2), length(lev) * nc), function(x) {
  do.call(rbind, rep(list(m2[x:(x + length(lev) * nc - 1)]), nc))
}))

yl <- seq(pp$yl2[1], pp$yl2[2], 10)
ylcol <- c("black", "grey", "black", rep("grey", 5), "black")
lt <- c(5, 1)
ylwd <- c(1.5, 2)

pdf(full_path(p_fig, "biases_1-200km.pdf"), width = 7.5, height = 7)
l <- layout(m3)
# i <- 1; j <- 1
par(mar = c(0.5, 0, 1, 0.3), oma = c(5, 4, 2, 2))
for(i in 1:length(snms)) {
  highcounter <- rep(0, length(lev))
  for(j in 1:length(lev)) {
    plot(pp$x, pp$y, ylim = pp$yl2, xlim = pp$xl, type = "l", lwd = 1, 
         axes = FALSE, xlab = "", ylab = "", xaxs = "i")
    for(z in 1:length(yl)) {
      lines(pp$x, rep(yl[z], 2), lwd = pp$y2lwd, col = ylcol[z])
    }
    muv <- rep(NA, 2)
    for(bt in 1:2) {
      d <- dstats_all[[bt]][[i]][[j]]
      n <- nrow(d)
      lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = ylwd[bt], 
            lty = lt[bt])
      muv[bt] <- round(mean(d[, 8], na.rm = TRUE))
      toohigh <- which(d[, "mu"] > pp$yl2[2])
      if(length(toohigh) > 0) {
        highcounter[j] <- 1
        xi <- toohigh[which.max(d[toohigh, "mu"])]
        text(xi, y = pp$yl2[2] + 4, labels = round(d[xi, "mu"]), cex = 1.1,
             col = "grey50", xpd = NA)
      }
    }
    text(5, pp$yl2[2] - 14, labels = paste(muv, collapse = " / "), cex = 1.1, 
         col = "grey10")
    if(j == 1) axis(2, at = yl, labels = yl, las = 2, mgp = c(1, 0.6, 0))
    if(j == 1) mtext(lcnms[i], side = 2, line = 2.8, cex = 1, col = cols[i])
    if(i == 1) mtext(levnms[j], side = 3, line = -0.4, cex = 1.2)
    axis(1, at = c(1, 5, 10, 15, 20), labels = rep("", 5), mgp = c(1, 1, 0), 
         tcl = -0.7, lwd.ticks = 1.2, pos = pp$yl2[1])
    axis(1, at = 1:20, labels = rep("", 20), las = 2, mgp = c(1, 0.4, 0), 
         tcl = -0.3, pos = pp$yl2[1])
    if(i == length(snms)) {
      axis(1, at = 1:20, labels = pp$xaxl2, las = 2, mgp = c(1, 0.8, 0), 
           tcl = -0.3, pos = pp$yl2[1])
    }
  }
}
mtext("% bias", side = 2, line = 2.1, cex = 0.8, outer = TRUE, adj = 0.5)
mtext("% cropland", side = 1, outer = TRUE, line = 1.5, cex = 0.8)
par(xpd = NA)
x <- grconvertX(0.75, from = "ndc", to = "user")
y <- grconvertY(0.07, from = "ndc", to = "user")
legend(x = x, y = y, legend = c("actual bias", "absolute bias"), lty = lt, 
       lwd = ylwd, bty = "n", cex = 1.2)
dev.off()

# DF <- do.call(rbind.data.frame, lapply(snms[-2], function(x) {
#   dstats_all[[2]][[x]]$f25[, c(1, 8)]
# }))
# dlm <- lm(mu ~ poly(V1, degree = 2), data = DF)
# plot(DF[, 1], DF[, 2])
# lines(predict.lm(dlm, newdata = data.frame("V1" = 1:100)))

# for(bt in 1:2) {
#   pdf(full_path(p_fig, btype[bt]), width = 7, height = 7)
#   lmat <- rbind(m, m3)
#   l <- layout(lmat)
#   par(mar = c(3, 0, 0, 0), oma = c(3, 4, 2, 2))
#   snms <- names(dstats_all[[bt]])[names(dstats_all[[bt]]) != "glcsh"]
#   dset <- dstats_all[[bt]][snms]
#   for(i in 1:length(snms)) { i
#     #bt <- 1
#     d <- dset[[snms[i]]]$f1
#     n <- nrow(d)
#     plot(pp$x, pp$y, ylim = pp$yl[[bt]], xlim = pp$xl, type = "l", 
#          lwd = pp$y1lwd[[bt]], axes = FALSE, 
#          xlab = "", ylab = "")
#     if(i == 1) axis(2, at = pp$yax1[[bt]], labels = pp$yax1[[bt]], las = 2, 
#                     mgp = c(1, 0.6, 0))
#     axis(1, at = 1:20, labels = pp$xaxl, las = 2, mgp = c(1, 0.4, 0), 
#          tcl = -0.3, pos = pp$yaxp[[bt]], cex = 0.8)
#     for(z in 1:length(pp$y2[[bt]])) {
#       lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd =pp$y2lwd, col = pp$y2lc[[bt]][z])
#     }
#     for(k in 1:n) {
#       a <- seq(grep("2.5", colnames(d)), by = 1, length.out = 6)
#       if(!is.na(d[k, 2])) {
#         boxplot_v(k, d[k, a], n, 150, 10, bcol, fcol, pcex = 0.5, 
#                   lwd = c(1, 0.5, 2))
#       }
#     }
#     lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = 3)
#     if(i == 1) mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, 
#                      line = 2.2, cex = 0.8)
#     mtext(lcnms[i], side = 3, line = 0, col = cols[i])
#   }
#   mtext("% cropland", side = 1, outer = TRUE, line = -36.7, cex = 0.8)
#   par(mar = c(0.5, 0, 0.5, 0.3))
#   for(i in 1:length(snms)) {
#     highcounter <- rep(0, length(lev))
#     for(j in 1:length(lev)) {
#       plot(pp$x, pp$y, ylim = pp$yl2[[bt]], xlim = pp$xl, type = "l", lwd = 1, 
#            axes = FALSE, xlab = "", ylab = "", xaxs = "i")
#       for(z in 1:length(pp$y2[[bt]])) {
#         lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd = pp$y2lwd, 
#               col = pp$y2lc[[bt]][z])
#       }
#       d <- dset[[i]][[lev[j]]]
#       n <- nrow(d)
#       lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = pp$y3lwd[j])
#       muv <- round(mean(d[, 8], na.rm = TRUE))
#       if(j == length(lev)) {
#         mtext(expression(mu), side = 1, cex = 0.8, col = "grey10", 
#               line = ifelse(bt == 1, -1.5, -1.8), adj = 1.1)
#       }
#       text(10, pp$yl2[[bt]][1] + 10, labels = muv, cex = 1.3, col = "grey10")
#       toohigh <- which(d[, "mu"] > pp$yl2[[bt]][2])
#       if(length(toohigh) > 0) {
#         highcounter[j] <- 1
#         xi <- toohigh[which.max(d[toohigh, "mu"])]
#         text(xi, y = pp$yl2[[bt]][2], labels = round(d[xi, "mu"]), 
#              col = "grey50", xpd = NA)
#       }
#       if(j == length(lev)) {
#         if(sum(highcounter) > 0) {
#           mtext("max", side = 3, cex = 0.7, col = "grey50", line = -0.7, 
#                 adj = 1.1)
#         }
#       }
#       if(j == 1) {
#         axis(2, at = seq(pp$yl2[[bt]][1], pp$yl2[[bt]][2], 10), 
#              labels = pp$yax2[[bt]], las = 2, mgp = c(1, 0.6, 0))
#       }
#       if(i == 1) mtext(levnms[j], side = 3, line = -0.4, cex = 0.8)
#       axis(1, at = c(1, 5, 10, 15, 20), labels = rep("", 5), mgp = c(1, 1, 0), 
#            tcl = -0.7, lwd.ticks = 1.2, pos = pp$yl2[[bt]][1])
#       axis(1, at = 1:20, labels = rep("", 20), las = 2, mgp = c(1, 0.4, 0), 
#            tcl = -0.3, pos = pp$yl2[[bt]][1])
#       if(i == length(snms)) {
#         axis(1, at = 1:20, labels = pp$xaxl2, las = 2, mgp = c(1, 0.8, 0), 
#              tcl = -0.3, pos = pp$yl2[[bt]][1])
#       }
#     }
#   }
#   mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, line = 2.2, 
#         cex = 0.8, outer = TRUE, adj = 0.35)
#   mtext("% cropland", side = 1, outer = TRUE, line = 1.5, cex = 0.8)
#   dev.off()
# }
